\documentclass[]{deedy-resume-openfont}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Sarwesh}{Shah}{ \href{mailto:sarweshshah@yahoo.com}{sarweshshah@yahoo.com} | 091.888.403.0830 \\
\urlstyle{same}{128, DSR Elite, Mahadevapura, Bengaluru} | 
\href{https://www.facebook.com/sarweshshah}{fb.co/sarweshshah}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{BITS Pilani}
\descript{B.E. Hons. Computer Science}
\location{2010 - 2014 | Pilani, Rajasthan}
Conc. in Software Engineering \\
Vidya Vihar Campus \\
MCN Scholarship (All Semesters) \\
\location{ Cum. GPA: 7.0 / 10.0}
\sectionsep

\subsection{Vidya Mandir}
\location{Grad. May 2010 |  Kota, India}
\sectionsep

\subsection{HM Education Centre}
\location{Grad. May 2008 |  Kolkata, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/sarweshshah}{\custombold{sarweshshah}} \\
LinkedIn://  \href{https://www.linkedin.com/in/sarweshshah/}{\custombold{sarweshshah}} \\
YouTube://  \href{https://www.youtube.com/c/SarweshShah}{\custombold{SarweshShah}} \\
Twitter://  \href{https://twitter.com/sarweshshah}{\custombold{@sarweshshah}} \\
Quora://  \href{https://www.quora.com/profile/Sarwesh-Shah}{\custombold{Sarwesh-Shah}}\\
Behance:// \href{https://www.behance.net/sarweshshah}{\custombold{sarweshshah}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}


\subsection{MAJOR COURSES}
Data Structures \& Algorithms \\
Computer Networks \\
{\footnotesize \textit{\textbf{(Computer Lab Volunteer) }}} \\
DataBase Systems \\
Theory of Computation \\
Digital Electronic Comp. Org. \\
Programming Language \& Compiler Construction + Practicum\\
\sectionsep

\subsection{ELECTIVES}
Data Communication \& Networking \\
Fuzzy Logic \& Neural Networks Application \\
Print \& Audio-Visual Advertisement \\
Introductory Psychology \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
JavaScript \textbullet{} NodeJS \textbullet{} ReactJS\\ 
 \textbullet{} HTML \textbullet{} CSS \textbullet{} Java  \\ 
\location{Moderate:}
C \textbullet{} C++ \textbullet{} Shell \textbullet{} iOS \textbullet{} C\#\textbullet{} WPF\\
Objective-C \textbullet{} Objective-C++ \\
\location{Familiar:}
Ansible  \textbullet{} Android \textbullet{} MySQL\textbullet{} Python\\
Unity \textbullet{} Blend \textbullet{} Xcode \textbullet{} Photoshop
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{}
I am a Computer Science graduate interested in combining computer graphics, arts and architecture. Currently, I work at PayPal India where I design and program intuitive user experiences and develop techniques that help visualize data for better comprehension.
\section{Experience}

\runsubsection{PayPal}
\descript{| Software Engineer }
\location{January 2015 – Present | Bengaluru, India}
\vspace{\topsep}
\custombold{Free Return Shipping (Front-End)} Enables PayPal customers to receive free return shipments. Led the mid-tier and designed the front-end for raising and viewing new return requests from ground up.
\begin{tightemize}
\vspace{\topsep}
\item Currently deployed in France, Canada, Australia with a combined user base of around 8 million.
\item All code was reviewed, perfected, and pushed to production.
\item Technology used - ReactJS, NodeJS, Kraken, jQuery
\end{tightemize}
\vspace{\topsep}

\custombold{Prism: A Service Operability Tool (Pilot)} Prism enables PayPal service owners and dependent engineers to quickly monitor their services, manage campaigns and pinpoint errors in code.
\begin{tightemize}
\item Currently, multiple internal services are enrolled, tested and deployed on the stand-alone live clusters.
\item Tech. used - Linux, Elasticsearch, Kibana, NodeJS
\end{tightemize}

\sectionsep
\vspace{\topsep}

\runsubsection{AUTODESK}
\descript{| Research \& Development Intern }
\location{June 2013 – December 2013 | Pune, India}
\begin{tightemize}
\item Implemented video and user interaction recording feature for CAD based iOS application, 123D Design.
\item Graphical calculator – application in line with assignments set by Prof Paul Hegarty for Stanford iOS Programming course.
\item Tech. used - OpenGL, Objective-C, Cocoa Touch, AVFoundation, Xcode
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Multimedia \& HCI Lab}
\descript{| Undergrad Research Assistant}
\location{January 2014 – May 2014 | Pilani, India}
\vspace{\topsep}
\custombold{Investigation into EdX architecture and Automation of Deployment of Django platform using Ansible on Cloud-based Environment} \\
Final-year project under the mentorship of Pranjal Ranjan and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Rahul Banerjee}}. 
The project results were later used to implement the e-Learning website of BITS Pilani.
Created Ansible play-books to automate deployment of Open EdX modules on university cloud. Technology used - Django, Ansible, Hybrid cloud deployment
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS & AFFILIATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{AWARDS \& AFFILIATIONS} 
\begin{tightemize}\vspace{\topsep}
\item Winner of spot award in various company-wide hackathons held in PayPal.
\item Senior Diploma in Painting from Bangiya Sangeet Parishad (Ankan Kala Vibhag) \& have been a scholar of Indian Fine Arts Association.
\item Senior Member of the Photography Club, BITS Pilani since August 2010 contributing and exhibiting my photographs in half-yearly exhibitions and delivered mentor lectures for photography enthusiasts in college.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}
